---
title: "Case_impact_final"
Author: Hossain Morhed
output: html_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#clearing the environment

```{r}
rm(list=ls(all=TRUE))
```

#Loading the "Tidyverse" library, if the library does not exist it will install the library after it loads the library. 

```{r}
if(!require("tidyverse")){
  install.packages("tidyverse")
}

library(tidyverse)
```

# Upload Semicolon-separated CSV files into the environment.

```{r}
case_data <- read.csv("extend_case_data.csv",sep = ";")
head(case_data)

```


# summary of the table
```{r}
summary(case_data)

```

# we are checking the data type and checking the missing value.
# In R, missing values are represented by the symbol NA (not available). Impossible values (e.g., dividing by zero) are represented by the symbol NaN (not a number).
```{r}

glimpse(case_data)

#colSums(is.na(raw_case_data))
#colSums(raw_case_data=="")
```


```{r}
colSums(is.na(case_data))
```


```{r}
colSums(case_data=="")

```

# converting date column from factor to date.

```{r}
case_data$date<-as.Date(case_data$date, format="%d-%m-%Y")

```


# converting date column from factor to date.

```{r}
#print(raw_case_data$date)

#case_data1<- raw_case_data %>% mutate(date_date = as.Date(raw_case_data$date, format="%d-%m-%Y"))
#case_data<-case_data1 %>% select(-date)

#case_data<-case_data1 %>% select(date_date,source_medium,campaign,currency,transactions,transaction_revenue)

#colnames(case_data)[1]<-"date"
#colnames(case_data)[which(names(case_data) == "date_date")] <- "date"
```

# Checking the data type again also the different types of currency present in our data set.

```{r}
glimpse(case_data)
table(case_data['currency'])

case_data %>% count(currency)

```

#part a: creating a column of specific date exchange rate or historical exchange rate
# Installing and loading the library quantmod

```{r}

if(!require("quantmod")){
  install.packages("quantmod")
}
library(quantmod)

```
# By using 'quantmod' we collect or download exchange rate data from Oanda. https://www.oanda.com/eu-en/
# Oanda, The Currency Site (FX and Metals)

# creating a list of currency combinations from the currency column of our data table and using it to download the September 2021 currency exchange rate. The exchange rate is in DKK.
```{r}

currCombinations = paste(setdiff(unique(case_data$currency),"DKK"),"DKK",sep="/")

for (i in currCombinations){
  #print(i)
  getFX(i,from="2021-09-01", to="2021-09-30")
}

```

# creating an exchange rate column and filling each row with value 1. Exchange rate 1 DKK = 1 DKK

```{r}
case_data$exchange_rate<- 1
```

# Now we are filling the exchange rate column based on USD currency and date.
# All exchange rates are in DKK.

```{r}
row_number<- which(case_data$currency=="USD",arr.ind=TRUE)
#print(row_number)
selected_date<-c()
for (i in row_number){
  selected_date<-c(selected_date,case_data[i,"date"])
}
#print(selected_date)
e_rate<-c()
for (i in selected_date){
  e_rate<-c(e_rate,USDDKK[as.Date(i)])
}

exchange_rate_temp<-replace(case_data$exchange_rate,row_number,e_rate)
case_data$exchange_rate<- exchange_rate_temp
```

# Now we are filling the exchange rate column based on NOK currency and date.
# All exchange rates are in DKK.

```{r}
row_number<- which(case_data$currency=="NOK",arr.ind=TRUE)
#print(row_number)
selected_date<-c()
for (i in row_number){
  selected_date<-c(selected_date,case_data[i,"date"])
}
#print(selected_date)
e_rate<-c()
for (i in selected_date){
  e_rate<-c(e_rate,NOKDKK[as.Date(i)])
}

exchange_rate_temp<-replace(case_data$exchange_rate,row_number,e_rate)
case_data$exchange_rate<- exchange_rate_temp
```

# Now we are filling the exchange rate column based on SEK currency and date.
# All exchange rates are in DKK.

```{r}
row_number<- which(case_data$currency=="SEK",arr.ind=TRUE)
#print(row_number)
selected_date<-c()
for (i in row_number){
  selected_date<-c(selected_date,case_data[i,"date"])
}
#print(selected_date)
e_rate<-c()
for (i in selected_date){
  e_rate<-c(e_rate,SEKDKK[as.Date(i)])
}

exchange_rate_temp<-replace(case_data$exchange_rate,row_number,e_rate)
case_data$exchange_rate<- exchange_rate_temp
```

# Now we are filling the exchange rate column based on AUD currency and date.
# All exchange rates are in DKK.

```{r}
row_number<- which(case_data$currency=="AUD",arr.ind=TRUE)
#print(row_number)
selected_date<-c()
for (i in row_number){
  selected_date<-c(selected_date,case_data[i,"date"])
}
#print(selected_date)
e_rate<-c()
for (i in selected_date){
  e_rate<-c(e_rate,AUDDKK[as.Date(i)])
}

exchange_rate_temp<-replace(case_data$exchange_rate,row_number,e_rate)
case_data$exchange_rate<- exchange_rate_temp
```

# Now we are filling the exchange rate column based on EUR currency and date.
# All exchange rates are in DKK.

```{r}
row_number<- which(case_data$currency=="EUR",arr.ind=TRUE)
#print(row_number)
selected_date<-c()
for (i in row_number){
  selected_date<-c(selected_date,case_data[i,"date"])
}
#print(selected_date)
e_rate<-c()
for (i in selected_date){
  e_rate<-c(e_rate,EURDKK[as.Date(i)])
}

exchange_rate_temp<-replace(case_data$exchange_rate,row_number,e_rate)
case_data$exchange_rate<- exchange_rate_temp
```


# creating a column revenue_in_DKK

```{r}
case_data$revenue_in_DKK<- case_data$transaction_revenue*case_data$exchange_rate
```

# counting each item in the campaign column to get an overall idea.

```{r}
case_data %>% count(campaign)

```

# Creating a column based on Brand and Others, we filling each raw with Others

```{r}
#case_data$campaign_categori<- "Others"
library(tibble)
case_data<- add_column(case_data, campaign_categori = "Others", .after = "campaign")

```

# Finding appropriate row which is "00: brand" and replaces Others with Brand.

```{r}
case_data$campaign_categori[(str_detect(case_data$campaign,regex("00: brand",ignore_case = TRUE)))==1]<-"Brand"

```

# Counting the campaign_categori to make sure the code is working properly.

```{r}
case_data %>% count(campaign_categori)

```

# save the new table as a CSV file.

```{r}
write.csv(case_data,"case_data_final_v2.csv", row.names = FALSE)


```

# 

```{r}
#if(!require("xlsx")){
  #install.packages("xlsx")
#}
#library(xlsx)
#write.xlsx(case_data, "case_data_final.xlsx")

```


```{r}


```


```{r}


```




